
Substantive
author creds/abstract/conflict/funding disclaimer/edit Alex's acknowledgements 
Services to be completed or replaced with a sentence

Small edits
Page 3 - figure 2 (power) needs to be much larger or removed/dropped
in an appendix

Page 5 - figure 3+4 take up the page - should they be in an appendix/
are they readable etc.

Page 7 - 1.2.1 Bulk Materials - "producible on Mars in table ??" - ?? reference not loading?

Page 8 - the 3 images sitting together is odd - can we move the mining to 
the previous page so it sits under the correct section (and stops cluttering)

    - "Similarly, the iron powder is also refined throughiron carbonyl??to form pure iron powde" ?? reference not loading?

Page 16 - reference 4 is formatting wrongly (the misc long url one) 

@John:

1. I added one line at the end of immigration that links down to a new section titled "Critical Services". Please review both.
2. Architecture
3. Structure of the Market
Done.

@all
1. See my changes to the market for bulk materials they are substantive.
2. Page 5 - there is an odd paragraph break before 'TSSE is an attractive candidate..."
3. Page 6 - Figure 5 is oddly isolated on the page 
4. Page 7 - ZSI oxygen generator, powered bya mass-produced kilopower-style??reactor
5. Page 8 - Direct reduction iron is implemented as described in??using syngas regenerated via a Zn/S/I cycle reactor. 
6. Page 9 - . Similarly, the iron powder is also refined through
iron carbonyl ?? to form pure iron powder, which is suitable
for laser or electron beam 3d printing